---
title: "My First App Using Shiny Application"
author: "Ankit Pandey"
date: "2023-06-27"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(HistData)
library(ggplot2)
```


## About the Course Project
This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

- Write a shiny application with associated supporting documentation. 
- The documentation should be thought of as whatever a user will need to get started using your application.
- Deploy the application on Rstudio's shiny server
- Share the application link by pasting it into the provided text box
- Share your server.R and ui.R code on github


## How to use the application
Using the data provided by Galton Families dataset, we fit a linear model to predict a child's height based on the gender and parent's average height.

The application is running on 
(https://ankitp0199.shinyapps.io/MyFirstApp/)

ui.R, and Server.R Code in my github repository 
(https://github.com/ANKITP1999/My-First-Shiny-Application-and-Reproducible-Pitch.git)

## Galton Family Dataset

```{r cars, echo = TRUE}
data("GaltonFamilies")
head(GaltonFamilies)
summary(GaltonFamilies)
```

## Plot of GaltonFamilies

```{r GaltonFamilies}
g <- GaltonFamilies
ggplot(data=GaltonFamilies,aes(x=midparentHeight,y=childHeight,color=gender)) +
  geom_point()

```

